Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-07-16 grove-paper.tex
Updates from Overleaf

A deletes code that B is editing
Then A pastes it somewhere else

>>>>

Consider Figure~\ref{fig:Editing Nested Parts of the Code}.
Alice and Bob both start with the top graph, which represents the code \texttt{2 * x + \hole{}}.
Alice changes the \texttt{2} to a \texttt{3}, which results in the left graph.
Bob moves the \texttt{2 * x} from the left of the plus to the right of the plus
by deleting edge~7 and adding edge~16, which results in the right graph.
Since vertex and edge identifiers are preserved by these,
both Alice's and Bob's edits can be applied to the other's graph,
which results in both Alice and Bob having the bottom graph.

As with Subsection~SEC:TODO, this merge does not require coordination
between Alice and Bob.  They could independently send their edits
to a third party, Charley, who could replay their edits in any order
and will always get the bottom graph.

Supporting this kind of behavior is
